% Chapter 1: Project Overview (Operations Manager)
\chapter{Project Overview}

\section{What this platform is}
This is a travel booking platform. It connects three roles:
\begin{itemize}
  \item Admin: Oversees the system and users.
  \item Vendor: Lists and manages travel packages.
  \item Customer: Browses, books, pays, and leaves reviews.
\end{itemize}

\section{What the platform offers}
The platform supports three kinds of bookings:
\begin{itemize}
  \item Hotel
  \item Apartment
  \item Tour
\end{itemize}

\section{What is working now}
Below is a plain summary of what is already working.

\subsection*{Admin}
\begin{itemize}
  \item Vendor management: Review vendor applications and manage vendor listings.
  \item User management: View and manage user accounts.
  \item Monitor activity: View bookings, payments, and reviews at a high level.
  \item Review management: See and manage customer reviews.
\end{itemize}

\subsection*{Vendor}
\begin{itemize}
  \item Package management: Create and manage hotel, apartment, and tour packages.
  \item Booking management: See bookings for their packages.
  \item Withdraw funds: Request withdrawal of earnings.
  \item Refund handling: Start and track refund processes.
\end{itemize}

\subsection*{Customer}
\begin{itemize}
  \item Browse and book: Find packages and make bookings.
  \item Pay: Make secure payments.
  \item Review: Leave feedback after a booking.
\end{itemize}

\section{Notes}
This overview avoids technical details. It shows what the platform does today for each role. Next, we will outline the pending work and the reasons for delays.


