% Chapter 2: Pending Work (Operations Manager)
\chapter{Pending Work}

\section{Main gap: Notification system}
The key item left is the notification system. This should help all users get timely updates about important actions. It should be simple, clear, and consistent.

\section{Who should receive notifications}
\begin{itemize}
  \item Admin: New vendor requests, high-risk payments, refund requests, dispute flags.
  \item Vendor: New bookings, payment received, payout status, new reviews, refunds.
  \item Customer: Booking status, payment status, refund status, review confirmation.
\end{itemize}

\section{When notifications should be sent}
\begin{itemize}
  \item Booking created, confirmed, or cancelled.
  \item Payment created, succeeded, or failed.
  \item Refund requested, approved, or rejected.
  \item Review submitted.
  \item Vendor application submitted or decided.
\end{itemize}

\section{How notifications should appear}
\begin{itemize}
  \item In-app notifications: Visible in each user dashboard.
  \item Email (optional): For key events like payment or booking confirmation.
\end{itemize}

\section{Simple acceptance checklist}
The notification system is “done” when the following checks pass:
\begin{itemize}
  \item Clear list of events and recipients is documented.
  \item In-app notifications show for Admin, Vendor, and Customer.
  \item Emails (if used) send for payment and booking confirmations.
  \item Notifications link back to the right record (booking, payment, review, vendor request).
  \item A basic settings page exists to mark notifications as read.
  \item Test cases run: create booking, payment success, refund request, review add, vendor approval.
\end{itemize}

\section{Small cleanups (if time allows)}
\begin{itemize}
  \item Final pass on labels and messages to keep wording simple.
  \item Quick UI check for consistency in dashboards.
\end{itemize}


