% Chapter 3: Timeline and Delay Analysis (Operations Manager)
\chapter{Timeline and Delay Analysis}

\section{Short timeline}
\begin{itemize}
  \item Dec 17, 2024: Initial user flow design (7 days, \$100).
  \item Jan 4, 2025: Expanded to 10-page design with detailed flow.
  \item Jan 31, 2025: Added 6 more UI pages.
  \item Feb 5, 2025: Added 10 more UI pages.
  \item Mar 5, 2025: Final 10-page UI completion.
  \item April 2025: Frontend development started.
  \item June 2025: Backend development started (in parallel with frontend).
\end{itemize}

\section{Why the project was delayed}
\subsection*{1. Scope growth}
The work grew from a small 7-day design to a much larger build. The total value increased from \$100 to \$1{,}980 across five orders. This added more pages, more flows, and more features than first planned.

\subsection*{2. Frontend and backend in parallel}
Both sides ran at the same time. This created timing issues. When the backend changed, the frontend had to change. When the frontend changed, the backend had to adjust. This caused loops of rework.

\subsection*{3. Integration rework}
After the backend started in June, we found many points that did not match the frontend. This required many rounds of updates.

\subsection*{4. Unclear or changing requirements}
Some key business rules were not clear in the UI design phase. These items needed rethinking and rework:
\begin{itemize}
  \item How a package should be created step by step.
  \item How a vendor should be created and verified.
  \item How the full payment flow should work end to end.
  \item Missing details for tour management.
\end{itemize}

\subsection*{5. Resource loss}
The original UI designer left. This made UI updates and design alignment harder and slower.

\subsection*{6. Cascading changes}
When we changed the backend, the frontend had to change. When the frontend changed, the UI and content also needed updates. This repeated several times and added more delay.

\section{Impact in simple terms}
\begin{itemize}
  \item Time: A short design job became a multi-month build.
  \item Workload: Extra reviews, meetings, and rework across teams.
  \item Risk: Without clear rules and a scope freeze, delays can repeat.
\end{itemize}


