% Chapter 4: Conclusion and Actions (Operations Manager)
\chapter{Conclusion and Actions}

\section{Where we stand}
The core of the platform is in place. Admin, Vendor, and Customer can each do their main tasks. The main missing piece is the notification system. This is the last big item to make the platform feel complete and responsive.

\section{What we need to finish}
\begin{itemize}
  \item Finalize notification events, recipients, and messages.
  \item Implement in-app notifications for all roles.
  \item (Optional) Enable email notices for key events like payments and bookings.
  \item Test end to end with booking, payment, review, and vendor flows.
\end{itemize}

\section{Actions for operations}
\begin{itemize}
  \item Approve the notification plan and wording (short, simple messages).
  \item Freeze scope for MVP until notifications are done and tested.
  \item Confirm the four business rules that were unclear earlier:
    \begin{itemize}
      \item Package creation steps.
      \item Vendor creation and verification steps.
      \item Payment flow end to end.
      \item Tour management details.
    \end{itemize}
  \item Set a weekly check-in to track only these items and testing.
\end{itemize}

\section{Target delivery window}
Once the notification plan is approved, we can complete implementation and testing in a short, focused window. We will provide an exact date after sign-off on the plan and messages.

\section{Close}
This report is meant to be simple and direct. The goal is to finish the single missing system, verify the key business rules, and deliver the MVP with confidence.


